Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-10-13 causal-bandit/nips_2016/additional_experiments.tex
updates experiment figuresq

Unknown to the algorithms, $Y$ depends only on $X_1$ and $X_N$. 
\eq {
P(Y|\boldsymbol{X}) = \begin{cases} 
a & \text{ if } X_1=0,X_N = 0 \\
b & \text{ if } X_1=0,X_N = 1 \\
c & \text{ if } X_1=1,X_N = 0 \\
d & \text{ if } X_1=1,X_N = 1 \\
\end{cases}
}

We then vary $N_1$ from 2 to $N$ to vary $m$. The values for the CPD's have been chosen such that we can analytically calculate $\eta*$. This allows us to just show the dependence on $m$, removing the noise associated with different models producing selecting values for $\eta$ with the same $m$ (and thus same worst case performance) but different performance for a given reward distribution.

@@

In figure \ref{fig:simple_vs_T_misspecified} we exclude actions on $Z$ from the set of allowable actions to demonstrate how algorithm 1 can fail in the presence of a hidden confounding variable. Algorithm 1 incorrectly assumes $P(Y|do(X)) = P(Y|X)$ leading to biased estimates. 
\eq{
P(X_i = 1|Z = 0) &= \begin{cases} 0 & \text{ if } i \in \set{1,...N_1} \\ .4 & \text{ otherwise } \end{cases}\\
P(X_i = 1|Z = 1) &= \begin{cases} 0 & \text{ if } i \in \set{1,...N_1} \\ .65 & \text{ otherwise } \end{cases}
}

These values have been chosen to show the worst case, where the bias results in Algorithm 1 asymptotically selecting a non-optimal action.

\begin{figure}[H]
    \begin{subfigure}[t]{0.3\textwidth}
		\centering    
    		\includegraphics[width=\textwidth]{exp_regret_vs_m_N50_T400_s10000_20160519_1030.pdf}
    		\caption{Simple regret vs $m(\eta*)$ for fixed horizon $T=400$ and number of variables $N = 50$}
        \label{fig:simple_vs_m_general}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{experiment2_N50_a4_s10000_20160519_1030.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and $\epsilon = \sqrt{\frac{N}{8T}}$}
        \label{fig:simple_vs_T_general}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{experiment3_N50_s10000_20160519_1030.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and fixed $\epsilon = .3$}
    		\label{fig:simple_vs_T_misspecified}
    \end{subfigure}
    \caption{Experimental results on the confounded graph}
    \label{fig:experiments}
\end{figure}

>>>>

As in the parellel bandit case, we let $Y$ depend only on $X_1$, $P(Y|do(X_1)=1) = \frac{1}{2} + \epsilon$ amd $P(Y|do(X_1=0)) = \frac{1}{2}-\epsilon'$, where $\epsilon' = \epsilon\frac{P(X_1=1)}{P(X_1=0)}$. We vary $N_1$ from 2 to $N$ to vary $m$. The values for the CPD's have been chosen such that the reward distribution is independent of $m$ and so that we can analytically calculate $\eta*$. This allows us to just show the dependence on $m$, removing the noise associated with different models producing selecting values for $\eta*$ with the same $m$ (and thus same worst case performance) but different performance for a given reward distribution.

@@

In figure \ref{fig:simple_vs_T_misspecified} we exclude actions on $Z$ from the set of allowable actions to demonstrate how algorithm 1 can fail in the presence of a hidden confounding variable. Algorithm 1 incorrectly assumes $P(Y|do(X)) = P(Y|X)$ leading to biased estimates. To show the worst case outcome, where this bias results in Algorithm 1 asymptotically selecting a sub-optimal action, we need a slightly more complex CPD's.

\eq{
P(X_i = 1|Z = 0) &= 
\begin{cases} 
.166 & \text{ if } i \in \set{1,...6} \\
.2 & \text{ if } i = 6 \\
.7 & \text { otherwise} 
 \end{cases}\\
 P(X_i = 1|Z = 1) &= 
\begin{cases} 
.166 & \text{ if } i \in \set{1,...6} \\
.8 & \text{ if } i = 6 \\
.3 & \text { otherwise} 
 \end{cases}\\
}

$Y$ depends only on $X_6$ and $X_N$. 
\eq {
P(Y|\boldsymbol{X}) = \begin{cases} 
a & \text{ if } X_6=0,X_N = 0 \\
b & \text{ if } X_6=0,X_N = 1 \\
c & \text{ if } X_6=1,X_N = 1 \\
d & \text{ if } X_6=1,X_N = 0 \\
\end{cases}
}

\begin{figure}[H]
    \begin{subfigure}[t]{0.3\textwidth}
		\centering    
    		\includegraphics[width=\textwidth]{experiment4_20161012_1536.pdf}
    		\caption{Simple regret vs $m(\eta*)$ for fixed horizon $T=400$ and number of variables $N = 50$}
        \label{fig:simple_vs_m_general}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{experiment7_20161012_1147.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$ and $m(\eta*)=3.1$ }
        \label{fig:simple_vs_T_general}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{experiment3_N50_s10000_20160519_1030.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=xx$ with no actions setting $Z$}
    		\label{fig:simple_vs_T_misspecified}
    \end{subfigure}
    \caption{Experimental results on the confounded graph}
    \label{fig:experiments}
\end{figure}
